\documentclass[a4paper,11pt]{letter}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\topmargin=-0.5in  

\begin{document}
	\begin{letter}{\bf Physical Review Fluids}
		
		\opening{To whom it may concern,}
		
		We hope all is well with you, and we thank you for assisting us with this submission.
		
		Please find attached our manuscript entitled ``On Data-Driven Methods for Buoyancy-Driven Rising Bubble within Eulerian, Lagrangian, and Moving-Eulerian Frames.'' In this work, we systematically evaluate the accuracy of Proper Orthogonal Decomposition (POD) and Dynamic Mode Decomposition (DMD) for reduced-order modeling of the convection-dominated rising bubble problem, using direct numerical simulation data within Eulerian, Moving-Eulerian, and Lagrangian frameworks. The manuscript demonstrates how a change of observer impacts the accuracy of bubble interface reconstruction, rise velocity, and trajectory estimation. Furthermore, it shows that POD consistently outperforms DMD across the rectilinear, transitional, and oscillatory stages of bubble rise.
		
		Overall, our study aims to bridge the growing role of data-driven approaches in fluid mechanics with their practical application to multiphase flow problems. We believe our findings offer new insights into the applicability and limitations of these methods in different frames.
		
		All authors have approved the submission and there are no conflicts of interest to declare.
		
		Thank you for considering our submission.
		
		With kind regards,\\
		Behnam Kazemi Majd and co-authors.
		
	\end{letter}
\end{document}
